### 2017-08-13 doc/MSc-dissertation.tex
Results

In order to obtain the characteristic length scale relevant to the system (\textbf{integral scale}), eqn.~\ref{eq2.5} is used. This describes the correlation of the fluctuating component of the velocity field at the large scales. This is then used to obtain the Reynolds number~\cite{mccomb1990physics}. To do so, a corresponding characteristic velocity needs to be defined. Since the type of turbulence that is being studied is HIT, it is possible to take the root-mean-squared velocity to be the aforementioned characteristic velocity. This rms velocity is defined with the kinetic energy $E_K=\frac{1}{2}(u_x^2+u_y^2+u_z^2)=\frac{3}{2}u_{rms}^2$ since the isotropy condition requires rotational invariance, and thus $\langle u_x \rangle = \langle u_y \rangle = \langle u_z \rangle$.

@@

A smaller length scale that determines the inertial range mentioned above is the \textbf{Taylor length scale}. It is also referred to as the turbulent length scale for this very reason. With the energy dissipation rate as $\varepsilon$, and the kinetic viscosity $\nu$, the Taylor microscale is defined~\cite{LinkmannMoritzFrederikLeon2016Spim}:

@@

Finally, the smallest length scales of the system are close to the \textbf{Kolmogorov microscale}. At this scale (large wave numbers), most energy is being dissipated into heat~\cite{mccomb1990physics}. Working through dimensional analysis it is possible to arrive at the following length scale related to viscous dissipation:

@@

In addition to the post-processing scripts mentioned above, several others were written to automate the use of \texttt{gnuplot} to perform graphs and heat maps, check for the existence of dynamo action in the end of every simulation, or obtain relevant values to each simulation. For example, and with the use of some information from the input file, the Kolmogorov microscales (along to their relation to the maximum wave number), Reynolds number, and magnetic Reynolds number with their appropriate statistical errors.

@@

A detailed account of the simulations that were generated, along with their motivations, is laid out here. The first simulation was done in a large box, $N^3=1024^3$, for which viscosity was ten times larger than magnetic diffusivity, i.e. $Pr_M=\nu/\eta=10$. As it was mentioned before, the magnetic Prandtl number compares the kinetic and the magnetic channel. That is, it compares how turbulent the magnetic field is relative to the velocity field, which is equivalent of comparing how much energy is dissipated through the magnetic channel against the kinetic channel.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.4\textwidth]{img/slices}
\caption{Magnetic energy for $Pr_M=500$, $\nu=5e-2$~\cite{schekochihin2004simulations}.}
\label{figure}
\end{figure}

>>>>

In order to obtain the characteristic length scale relevant to the system (\textbf{integral scale}), the longitudinal two-point correlation function of eqn.~\ref{eq2.5} is used. This value of $L$ describes the correlation of the fluctuating component of the velocity field at the large scales, and it is used to obtain the Reynolds number~\cite{mccomb1990physics}. To do so, a corresponding characteristic velocity needs to be defined. Since the type of turbulence that is being studied is HIT, it is possible to take the root-mean-squared (rms) velocity to be the aforementioned characteristic velocity. The rms velocity is defined with the kinetic energy $E_K=\frac{1}{2}(u_x^2+u_y^2+u_z^2)=\frac{3}{2}u_{rms}^2$ since the isotropy condition requires rotational invariance, and thus $\langle u_x \rangle = \langle u_y \rangle = \langle u_z \rangle = u_{rms}$.

@@

An intermediary length scale that describes the range where viscosity starts to become important (in comparison to the nonlinear term) is the \textbf{Taylor length scale}. It is also referred to as the turbulent length scale for this very reason. With the energy dissipation rate as $\varepsilon$, and the kinetic viscosity $\nu$, the Taylor microscale is defined~\cite{LinkmannMoritzFrederikLeon2016Spim}:

@@

Finally, the smallest length scales of the system are close to the \textbf{Kolmogorov microscale}. At this scale (large wave numbers), most energy is being dissipated into heat~\cite{mccomb1990physics}. The Kolmogorov microscale ``starts'' when the viscous term is equally important to the nonlinear term, i.e. $Re=1$. Working through dimensional analysis it is possible to arrive at the following Kolmogorov microscale related to viscous dissipation:

@@

In addition to the post-processing scripts mentioned above, several others were written to automate the use of \texttt{Gnuplot} to perform graphs and heat maps, check for the existence of dynamo action in the end of every simulation, or obtain relevant values to each simulation. For example, and with the use of some information from the input file, the Kolmogorov microscales (along to their relation to the maximum wave number), Reynolds number, and magnetic Reynolds number with their appropriate statistical errors. These additional post-processing scripts were performed using \texttt{Bash} and \texttt{Python}. Finally, \texttt{Paraview} was used in order to generate plots of the velocity and the magnetic fields for some simulations.

@@

A detailed account of the simulations that were generated, along with their motivations, is provided here. The first simulation was done in a large box, $N^3=1024^3$, for which viscosity ($\nu=0.005$) was ten times larger than magnetic diffusivity, i.e. $Pr_M=\nu/\eta=10$. As it was mentioned before, the magnetic Prandtl number compares the kinetic and the magnetic channel. That is, it compares how turbulent the magnetic field is relative to the velocity field, which is equivalent of comparing how much energy is dissipated through the magnetic channel against the kinetic channel.

For the simulation with $N^3=1024^3$ grid points, \texttt{Paraview}, a slice of the velocity and the magnetic fields' magnitude was plotted. Figure~\ref{fig5.1} shows this slice, where the magnetic field is clearly more fine-grained than the velocity field. Which is not surprising since the Kolmogorov microscales for this system are $k_\nu = 33$ and $k_\eta = 185$.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\textwidth]{{img/f_1024_0.005_10_fieldslice}.png}
\caption{Heat map of $\vert u \vert$ (left) and $\vert b \vert$ (right) of a vertical  slice of a $N^3=1024^3$ box ~\cite{schekochihin2004simulations}.}
\label{fig5.1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{img/k3halfs}
\caption{Magnetic energy for $Pr_M=500$~\cite{schekochihin2004simulations}.}
\label{figure}
\end{figure}
